Seldin Report: Ssec Scores

### 2022-05-24 SeldinReport.Rmd
consolidation

brain.liv = bicorAndPvalue(ts_protein_brain, target_liver, use = 'pairwise.complete.obs')
# brain.liv$p

@@

>>>>

brain.liv = bicorAndPvalue(ts_protein_brain, target_liver, use = 'pairwise.complete.obs')

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
write.csv(brain.liv$p, "Bicor_brain.csv")
# brain.liv$p

@@

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
write.csv(liv.brain$p, "Bicor_liver.csv")
